Decentralised location proof system

### 2016-03-09 paper.tex
improving design section

\usepackage{tikz}
\usetikzlibrary{calc,arrows}
\usepackage{enumitem}

@@

When a node is created, it generates (or is provided with?) a certificate (or key pair). To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction. During the verification stage, the node will provide the verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions. The verifier calculates the node's identities using the public key and nonces, and retrieves the relevant transactions from the public blockchain. The verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.

@@

When a node is initialised, it must begin to record two \textit{Key Lists} for itself. A \textit{Key List} is a list of encryption keys previously used for transactions. For example, $KL_{A1}[n]$ and $KL_{A2}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively. These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.

@@

Where:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
\end{itemize}

@@

$P_An = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$

@@

\subsubsection{Key Packets}
The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt. However, in order to simultaneously preserve OTIT's ``provacy protected chronology'' property, the transaction backwards-chaining must not be broken. This is why two separate \textit{Key Lists} are maintained; $KL_{A1}$ is used to encrypt the backwards-chaining link, while $KL_{A2}$ encrypts the transaction data. For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
\\

\noindent
$KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\}, \ldots, \{KL_{BL}[m-n], KL_{BT}[m-n]\})$

@@

\subsection{Verification}
The verification stage is the most algorithmically complex part of the system. It is performed by the verifier. Given the keys for a node's $n$ most recent transactions, the verifier will walk chronologically backwards along the public location proof chain. At each transaction encountered, the search will fork along the proof history path of both parties involved in that transaction, and continue until all available transactions have been exhausted.

The goal of the verification stage is to either accept or reject the location that the user is claiming. There are a huge number of factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability. Some simple example factors may include:
\begin{itemize}
	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the verifier will reject his verification request.
	\item \textbf{Alibi reuse:} if the verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
	\begin{itemize}
		\item Due to transaction anonymity, the verifier may not always be able to tell if two alibi's are the same person or not. e.g. node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
		\item This is not a viable attack on the verification system. Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
	\end{itemize}
\end{itemize}

>>>>

\usepackage{tikz}
\usetikzlibrary{calc,arrows}
\usepackage{enumitem}
\usepackage{float}

@@

% add nonces and PK verification to the verify_request diagram! and discuss them below!

When a node is created, it generates a key pair. To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction. During the verification stage, the node will provide the verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions. The verifier calculates the node's identities using the public key and nonces, and retrieves the relevant transactions from the public blockchain. The verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.

@@

When a node is initialised, it must begin to record two \textit{Key Lists} for itself. A \textit{Key List} is a list of encryption keys previously used for transactions. For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively. These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.

@@

Where:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
\end{itemize}

@@

$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$

@@

\subsubsection{Key Packets} \label{sssec:key_packets}
The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt. However, in order to simultaneously preserve OTIT's ``provacy protected chronology'' property, the transaction backwards-chaining must not be broken. This is why two separate \textit{Key Lists} are maintained; $KL_{A1}$ is used to encrypt the backwards-chaining link, while $KL_{A2}$ encrypts the transaction data. For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
\\

\noindent
${KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\})}$

@@

\subsection{Verification}
\begin{minipage}{0.5\linewidth}
In the verification stage, a node tries to prove its location to a Verifier 3rd party, e.g. a bank. To do this, the node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
\begin{itemize}[noitemsep,topsep=0pt]
	\item[] $\mathbf{ID_{An-1}}$ is the ID of $A$'s most recently published transaction.
	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet from transaction $n-1$, and includes keys for as many transactions as $A$ feels is apropriate in order to receive verification.
	\item[] $\mathbf{loc}$ is $A$'s current claimed location for which it is seeking verification.
	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a list of the nonces used to generate $A$'s most recent IDs, from $n-1$.	
\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[c]{0.5\linewidth}
\begin{figure}[H]
\input{diagrams/verify_request.tex}
\caption{Verification request}
\label{fig:verify_request}
\end{figure}
\end{minipage}

The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming. Given $ID_{An-1}$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.

The Verifier uses $NP_{An-1}$ and $K^{+}_A$ to prove that node $A$ was the author of all of the transactions he claims to be. This prevents a collusion attack whereby nodes could share common transactions between different proof chains. When walking chronologically backwards along $A$'s proof chain, the 3rd party will ensure that the ID used in transaction $m$ on the proof chain matches $K^{+}_A(NP_{An-1}[m])$.

There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability and avoid gaming. Some simple example factors may include:
\begin{itemize}
	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the verifier will reject his verification request.
	\item \textbf{Alibi reuse:} if the verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
	\begin{itemize}
		\item Due to transaction anonymity, the verifier may not always be able to tell if two alibi's are the same person or not. e.g. node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
		\item This is not a viable attack on the verification system. Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
	\end{itemize}
\end{itemize}
